Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 discussion.tex

Our experience underscored the relevance of Heer and Agrawala's design
considerations, and indicated areas for further exploration. We adopt
their taxonomy for the following discussion.

{\bf Shared artifacts and artifact histories} are a central feature of
RCloud, through its shared workbooks of experiments and analyses.  We
observed that hackers readily share work through RCloud. They use it to
demonstrate techniques, share results with peers and managers, and transfer algorithms
to other groups.  Artifact histories can be accessed through the notebook
tree or through GitHub's web interface.

@@

{\bf Discovery is hard.}
While we have provided tools for searching and curating notebooks, the
search function does not help for finding methodology (and does not protect
searchers from erroneous notebooks), and the notebook tree starts to get
unwieldly with hundreds of users with hundreds of notebooks. In addition,
our choice to retain notebooks even when they have been deleted has
exacerbated the situation, since obsolete and broken notebooks stay around
forever.

@@

The system also needs to help users curate their notebooks. If a notebook
has been deleted or superceded by one of its forks, a user who opens it
should be warned. And operations on multiple notebooks and folders of
notebooks should be supported to make curation easier.

>>>>

Our experience underscored the relevance of Heer and Agrawala's design
considerations, and indicated areas for further exploration. We adopt
their taxonomy in the following discussion.

{\bf Shared artifacts and artifact histories} are a central feature of
RCloud, through its shared workbooks of experiments and analyses. We
observed that hackers readily share work through RCloud. They use it to
demonstrate techniques, share results with peers and managers, and to
transfer algorithms to other groups. Artifact histories can be accessed through the notebook
tree or through GitHub's web interface.

@@

{\bf Discovery is hard.}
While we have provided tools for searching and curating notebooks, the
search function does not help for finding methodology (and does not protect
searchers from erroneous notebooks), and the notebook tree starts to get
unwieldy with hundreds of users with hundreds of notebooks. In addition,
our choice to retain notebooks even when they have been deleted has
exacerbated the situation, since obsolete and broken notebooks stay around
forever.

@@

The system also needs to help users curate their notebooks. If a notebook
has been deleted or superseded by one of its forks, a user who opens it
should be warned. And operations on multiple notebooks and folders of
notebooks should be supported to make curation easier.

### 2015-03-31 relatedwork.tex

In some sense or another, the entire field of information
visualization and visual analytics revolve around improving how users
solve problems using data. In this section, we focus specifically on
system work relating to problem-solving enviroments and multiple users.

@@

An earlier study by Kandel et al argues that data wrangling
(cleaning, parsing and transformation)is a major part of exploratory
analysis and visualization~\cite{Kandel:2011:RDI}. We view this
as attacking a different semantic level than ours, but also
showing the need for an environment that enables better sharing
of the knowledge, tools and processes to do this. Anecdotally
we find much frustration among practitioners that this knowledge
is difficult to find and often isnot recorded or available in a
reusable form even within the same organization.

>>>>

In some sense or another, the entire field of information
visualization and visual analytics revolve around improving how users
solve problems using data. In this section, we focus specifically on
system work relating to problem-solving environments and multiple users.

@@

An earlier study by Kandel et al argues that data wrangling
(cleaning, parsing and transformation)is a major part of exploratory
analysis and visualization~\cite{Kandel:2011:RDI}. We view this
as attacking a different semantic level than ours, but also
showing the need for an environment that enables better sharing
of the knowledge, tools and processes to do this. Anecdotally
we find much frustration among practitioners that this knowledge
is difficult to find and often is not recorded or available in a
reusable form even within the same organization.
